Classical mechanics as the high-entropy limit \\ of quantum mechanics

### 2024-11-26 Articles/2024-ClassicalLimit/classicalLimitArticle.tex
ClassicalLimit: addressing comments

@@

>>>>

We focus on maps that increase the entropy uniformly because, in the end, we will want Hamiltonian evolution on the original states to correspond to Hamiltonian evolution on the transformed states. Since Hamiltonian evolution maps states at constant entropy, $S(R(\rho))$ must be a function of $S(\rho)$. Moreover, note that for any $\rho_1$ and $\rho_2$ with disjoint support, $S\left(\frac{1}{2}\rho_1 + \frac{1}{2}\rho_2\right) = 1 + \frac{1}{2}S\left(\rho_1\right) + \frac{1}{2}S\left(\rho_2\right)$. Since $R$ will preserve disjointness of support, the one bit of entropy increase will have to carry through the map, meaning that the difference in entropy will need to be preserved. This is why we are focusing on maps that increase the entropy uniformly.

@@

Note that while entropy could be increased in many different ways, under a stretching map unitary evolution will be mapped to another unitary evolution. In fact, if $H$ is a polynomial of position and momentum, we will be able to write the corresponding $\hat{H}$ such that $T_Q(\hat{H}) = H$. The stretching map, then, is useful to show not only that high-entropy states can be approximated by classical states, but that unitary evolution can be approximated by classical Hamiltonian mechanics. One may show that arbitrary entropy-increasing maps will recover classical states, for example by applying similar techniques to entropy bounds\cite{Hall_2018}, but they will not necessarily recover classical Hamiltonian evolution.
